---
title: "conditionals_loops.Rmd"
author: "Adelaide Robinson"
date: '2022-08-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
pm2_5 <- 48

if (pm2_5 < 100){
print("Low to Moderate Risk")
} else if (pm2_5 > 100 & pm2_5 < 150){
  print("Unhealthy for sensitive groups")
  } else 
      print("Health Risk Present")
```


```{r}
species <- "blue whale"
if (str_detect(species, "whale")) {
  print("You found a whale")
}
```
Create a vector stored as max_airtemp_c with a value of 24.1. Write an if else statement that will print “Temperature too high” if max_airtemp_c is greater than 27, or “Temperature OK” if temperature is less than or equal to 27.

```{r}
max_airtemp_c <- 26
if( max_airtemp_c > 27){
  print("Temperature too high")
} else if (max_airtemp_c <= 26){
  print("Temperature OK")
}
```
Store the base price of a burrito as base_burrito with a value of 6.50. Store main_ingredent with a starting string of “veggie.” Write a statement that will return the price of a burrito based on what a user specifies as “main_ingredient” (either “veggie”, “chicken” or “steak”) given the following:

    A veggie burrito is the cost of a base burrito
    A chicken burrito costs 3.00 more than a base burrito
    A steak burrito costs 3.25 more than a base burrito
    
    
```{r}
base_burrito <- 6.5
main_ingredient <- "steak"
if(str_detect(main_ingredient, "veggie")){
  print(base_burrito)
} else if (str_detect(main_ingredient, "chicken")){
  print(base_burrito + 3.00)
} else if (str_detect(main_ingredient, "steak")){
  print(base_burrito +3.25)
}
```

OR
```{r}
base_burrito <- 6.5
main_ingredient <- "veggie"
if(main_ingredient == "veggie"){
  print(base_burrito)
} else if (main_ingredient == "chicken"){
  print(base_burrito + 3.00)
} else 
  print(base_burrito + 3.25)

  
```
Create a new vector called fish that contains the values 8, 10, 12, 23 representing counts of different fish types in a fish tank (goldfish, tetras, guppies, and mollies, respectively). Write a for loop that iterates through fish, and returns what proportion of total fish in the tank are that species. Assume that these counts represent all fish in the tank.
```{r}
fish <- c(8, 10, 12, 23)

for (i in seq_along(fish)){
  val = fish[i]/ sum(fish)
  print(val)
  
}
```
There is an existing vector in R called month.name that contains all month names (just Try running month.name in the Console to check it out). Write a for loop that iterates over all months in month.name and prints “January is month 1,” “February is month 2”, etc.
```{r}
values <- seq_along(month.name)
for ( i in seq_along(month.name)){
  val = paste(month.name[i], "is month", values[i])
  print(val)
}
```

